Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Modified the table of objective types to reflect the new names
Broke up long lines

```{r}
larger_geographies_tally <- compact_data_with_citation_keys_no_fmd %>% 
    separate_rows(country_studied, sep = ' ') %>%
    distinct(title, country_studied, .keep_all = TRUE) %>%
    filter(country_studied %in% c('west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
    count(country_studied) %>% 
  arrange(desc(n)) %>% 
   adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()

knitr::kable(larger_geographies_tally, caption = 'Number of studies per location larger than one country', format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))

@@

#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
  group_by(country_studied) %>%
  summarise(num_of_studies = sum(num_of_studies),
            .groups = 'drop'
            ) %>% 
  filter(!country_studied %in% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
  arrange(desc(num_of_studies)) %>% 
  adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns() %>% 
  ungroup()

@@

```{r echo=FALSE}
#count the number of studies per objective type
modelling_objectives_count <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, objectives, name = 'num_of_studies') %>% 
  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('both', 'future', 'past')) %>% 
  adorn_pct_formatting(... = c('both', 'future', 'past')) %>% 
  adorn_ns(... = c('both', 'future', 'past'))

>>>>

```{r}
larger_geographies_tally <- compact_data_with_citation_keys_no_fmd %>% 
    separate_rows(country_studied, sep = ' ') %>%
    distinct(title, country_studied, .keep_all = TRUE) %>%
    filter(country_studied %in% c('west_africa', 'global', 
                                  'northern_hemisphere', 'southeast_asia', 
                                  'who_southeast_asia_region')
           ) %>% 
    count(country_studied) %>% 
  arrange(desc(n)) %>% 
   adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()

knitr::kable(larger_geographies_tally, 
             caption = 'Number of studies per location larger than one country', 
             format = "latex", booktabs = TRUE) %>% 
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

@@

#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
  group_by(country_studied) %>%
  summarise(num_of_studies = sum(num_of_studies),
            .groups = 'drop'
            ) %>% 
  filter(!country_studied %in% c('none', 'west_africa', 'global', 
                                 'northern_hemisphere', 'southeast_asia', 
                                 'who_southeast_asia_region')
         ) %>% 
  arrange(desc(num_of_studies)) %>% 
  adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns() %>% 
  ungroup()

@@

```{r echo=FALSE}
#count the number of studies per objective type
modelling_objectives_count <- compact_data_with_citation_keys_no_fmd %>% 
  count(collab_type, objectives, name = 'num_of_studies') %>% 
  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('prospective_analysis', 'retrospective_analysis')) %>% 
  adorn_pct_formatting(... = c('prospective_analysis', 'retrospective_analysis')) %>% 
  adorn_ns(... = c('prospective_analysis', 'retrospective_analysis'),
           position = "front")
